\huge Tor's Usability for Censorship Circumvention

### 2016-04-06 pets2017-paper/pets2017-paper.tex
add acknowledgements and uncited references
PETS2017 style.

\documentclass{template}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{hyperref}

\def\etal{{\it et al.~}}
\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}
\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

@@

%what I really want to say is that the interesting aspect of this usable design is that we had to 
%account for people who wouldn't need to use this launcher at all and also for at-risk users.
%... but in one catchy title. I can't think of one.
\title{Tor's Usability for Censorship Circumvention}
\numberofauthors{1}
\author{
 \alignauthor Linda N. Lee, David Fifield, Nathan Malkin \\
   \vspace{0.5em}
   \affaddr{University of California, Berkeley} \\
   \affaddr{\{lnl,fifield,nmalkin\}@cs.berkeley.edu}\\
}
\maketitle

\begin{abstract}
\indent \indent
Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool. It is now listed
as one of the ways that normal people use Tor \cite{whotor}.
We specifically examine its usability as a censorship circumvention tool,
an essential facet for adoption and use. We focus our analysis on the connection 
configuration interface of Tor Browser, as censorship circumvention requires 
correct transport configurations. We find that the Tor Browser 5.0.3. connection
configuration interface has a success rate of {\color {red} TODO}\% with the 
successful users having an average completion time of {\color {red} TODO} minutes. 
In this paper, we explore common challenges users faced during the configuration
process and redesign the interface to improve success rate to {\color {red} TODO}\% 
and average completion time to {\color {red} TODO} minutes.
\end{abstract}

\keywords{User Studies, Tor, Security, Censorship, Anonymity}

@@

\section {Acknowledgments}
{\color {red} TODO}

% Cecile Basnage for review of the UI of circumvention tools.

@@

\bibliographystyle{abbrv}
\bibliography{pets2017-paper}

@@

Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment.

\end{document}

>>>>

\documentclass[USenglish,oneside,twocolumn]{article}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
%\usepackage{hyperref}

\usepackage[utf8]{inputenc}%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
\usepackage[big]{dgruyter_NEW}

\DOI{foobar}

\cclogo{\includegraphics{by-nc-nd.pdf}}

@@

  \author*[1]{Linda Lee}

  \author[2]{David Fifield}

  \author[3]{Nathan Malkin}

  \author[4]{Ganesh Iver}

  \author[5]{Serge Egelman}

  \author[6]{David Wagner}

  \affil[1]{Affil, E-mail: lnl@cs.berkeley.edu}

  \affil[2]{Affil, E-mail: fifield@eecs.berkeley.edu}

  \affil[3]{Affil, E-mail: nmalkin@cs.berkeley.edu}

  \affil[4]{Affil, E-mail: ganesh.v@berkeley.edu}

  \affil[5]{Affil, E-mail: egelman@cs.berkeley.edu}

  \affil[6]{Affil, E-mail: daw@cs.berkeley.edu}

  \title{\huge Tor's Usability for Censorship Circumvention}

  \runningtitle{Tor's Usability for Censorship Circumvention}

  %\subtitle{...}

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool. It is now listed
as one of the ways that normal people use Tor \cite{whotor}.
We specifically examine its usability as a censorship circumvention tool,
an essential facet for adoption and use. We focus our analysis on the connection 
configuration interface of Tor Browser, as censorship circumvention requires 
correct transport configurations. We find that the Tor Browser 5.0.3. connection
configuration interface has a success rate of {\color {red} TODO}\% with the 
successful users having an average completion time of {\color {red} TODO} minutes. 
In this paper, we explore common challenges users faced during the configuration
process and redesign the interface to improve success rate to {\color {red} TODO}\% 
and average completion time to {\color {red} TODO} minutes.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

  \journalname{Proceedings on Privacy Enhancing Technologies}
\DOI{Editor to enter DOI}
  \startpage{1}
  \received{..}
  \revised{..}
  \accepted{..}

  \journalyear{2015}
  \journalvolume{2015}
  \journalissue{2}

\maketitle

@@

\section {Acknowledgments}
{\color {red} Rowie for setting up Xlab, Ganesh for helping us redesign the Interface, Nima, Isa, Georg, and the UX team for giving feedback, and Cecile for reviewing the UI of circumvention tools.}

% Rowie
% Ganesh
% Nima, Isa, Georg, Tor UX team. 
% Cecile Basnage for review of the UI of circumvention tools.

@@

\bibliographystyle{abbrv}
\nocite{*}
\bibliography{pets2017-paper}

@@

Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment. 
\end{document}
